A mixture of hidden Markov models to predict the lymphatic spread in head and neck cancer depending on primary tumor location

### 2024-01-28 content/manuscript.tex
sanitize graphics files in tex for overleaf

\includegraphics{manuscript_files/mediabag/../static/schematic_and_graph.pdf}

@@

\includegraphics{manuscript_files/mediabag/../figures/prevalence_by_subsite.pdf}

@@

\includegraphics{manuscript_files/mediabag/../figures/cluster_assignments.pdf}

@@

\includegraphics{manuscript_files/mediabag/../figures/prevalence_comparison.pdf}

>>>>

\includegraphics{manuscript_files/static/schematic_and_graph.pdf}

@@

\includegraphics{manuscript_files/figures/prevalence_by_subsite.pdf}

@@

\includegraphics{manuscript_files/figures/cluster_assignments.pdf}

@@

\includegraphics{manuscript_files/figures/prevalence_comparison.pdf}
